Tentative: On Open Data Releasing Protocols

### 2023-07-05 manuscript/main.Rnw

%% Make sure every package in preamble is used
\usepackage{siunitx} % for unit
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\numberwithin{equation}{section}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{underscore}
\usepackage{physics}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{threeparttable}
\usepackage{setspace}
\usepackage[width=.95\textwidth, skip=0.1\baselineskip]{caption}

\allowdisplaybreaks

% \usepackage{adjustbox}
\usepackage[colorlinks, citecolor=blue,  urlcolor=blue,
linkcolor=blue]{hyperref}
\usepackage{xcolor}

% \usepackage[pagewise]{lineno}
\usepackage[]{lineno}
\linenumbers*[1]
%% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
	\expandafter\let\csname old#1\expandafter\endcsname\csname
	#1\endcsname
	\expandafter\let\csname oldend#1\expandafter\endcsname\csname
	end#1\endcsname
	\renewenvironment{#1}%
	{\linenomath\csname old#1\endcsname}%
	{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
	\patchAmsMathEnvironmentForLineno{#1}%
	\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
	\patchBothAmsMathEnvironmentsForLineno{equation}%
	\patchBothAmsMathEnvironmentsForLineno{align}%
	\patchBothAmsMathEnvironmentsForLineno{flalign}%
	\patchBothAmsMathEnvironmentsForLineno{alignat}%
	\patchBothAmsMathEnvironmentsForLineno{gather}%
	\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

\allowdisplaybreaks % \usepackage{rotating}

\newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
\newcommand{\yh}[1]{\textcolor{purple}{YH: (#1)}}
\newcommand{\yx}[1]{\textcolor{cyan}{YX: (#1)}}
\let\proglang=\textsf
\newcommand{\pkg}[1]{{\fontseries{m}\selectfont #1}}
\newcommand\code[2][black]{\textcolor{#1}{\texttt{#2}}}

\usepackage{multirow, makecell}
\usepackage{booktabs,array}
\usepackage[affil-it]{authblk}
\renewcommand\Authfont{\fontsize{12}{14.4}\selectfont}
\renewcommand\Affilfont{\fontsize{12}{10.8}\itshape}
% \AddToHook{cmd/section/before}{\clearpage} % will remove

@@

\doublespacing

@@

Open data is the trend ... many kinds \citep[e.g.,][]{cdc2022} ...

@@

>>>>

\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{authblk}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}

\usepackage[]{lineno}
\linenumbers*[1]
%% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
	\expandafter\let\csname old#1\expandafter\endcsname\csname
	#1\endcsname
	\expandafter\let\csname oldend#1\expandafter\endcsname\csname
	end#1\endcsname
	\renewenvironment{#1}%
	{\linenomath\csname old#1\endcsname}%
	{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
	\patchAmsMathEnvironmentForLineno{#1}%
	\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
	\patchBothAmsMathEnvironmentsForLineno{equation}%
	\patchBothAmsMathEnvironmentsForLineno{align}%
	\patchBothAmsMathEnvironmentsForLineno{flalign}%
	\patchBothAmsMathEnvironmentsForLineno{alignat}%
	\patchBothAmsMathEnvironmentsForLineno{gather}%
	\patchBothAmsMathEnvironmentsForLineno{multline}%
}

@@

\newcommand{\jy}[1]{\textcolor{orange}{JY: (#1)}}
\newcommand{\yh}[1]{\textcolor{purple}{YH: (#1)}}
\newcommand{\yx}[1]{\textcolor{cyan}{YX: (#1)}}
\let\proglang=\textsf
%% \newcommand{\pkg}[1]{{\fontseries{m}\selectfont #1}}
%% \newcommand\code[2][black]{\textcolor{#1}{\texttt{#2}}}

@@

% \doublespacing

<<prep, echo=FALSE, cache=FALSE>>=
library(knitr)
## set font size
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  paste0("\n \\", "small","\n\n", x, "\n\n \\normalsize")
})
## read in all the chunks; so only need to maintain one place
read_chunk("../code/data_cleansing_311_V4.R")
@

@@

Open data is the trend ... many kinds \citep{barns2016mine}

@@

We need to make the variable names user friendly:
<<makeColNamesUserFriendly>>=

@
